\noindent 
Bioinformatics is an interdisciplinary field that utilizes biology, computer science, mathematics, and statistics to store and analyze biological data. With the completion of the Human Genome Project and the advent of the post-genomic era, proteomics research has become one of the most important areas of life sciences. Proteomics involves studying the characteristics of proteins to describe their structure, function, and role in regulating biological systems. Proteins often do not act alone but interact with each other, forming larger molecular complexes to perform biological functions. These interactions are represented using a network structure called the protein-protein interaction (PPI) network. A protein complex in PPI networks is a molecular structure composed of proteins that are functionally and structurally compatible. By analyzing PPI networks, we can identify these groups of proteins.

One of the key challenges in bioinformatics is the discovery of protein modules in protein-protein interaction networks. Identifying these modules is equivalent to the problem of community detection in graphs. In many bioinformatics applications, protein module discovery is performed using community detection algorithms in graphs. In this study, we aim to design a specialized method for community detection in protein interaction networks that, in addition to considering the graph structure for module identification, also takes into account the biological characteristics of proteins.

For example, integrating biological information about proteins stored in databases such as GO and KEGG with gene expression data and combining this information with the PPI network can enhance the accuracy and efficiency of protein module identification. Therefore, in this research, we aim to introduce a clustering algorithm for PPI networks based on graph neural networks while incorporating node-specific features.

\latinkeywords{Graph Neural Networks, Protein-Protein Interactions, Functional Module Identification, Clustering Attributed Graphs}
